---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- README.md is generated from README.Rmd. Please edit that file -->

# Inside Dogfish Stock Assessment for British Columbia

## Install dependencies

### GitHub R packages

```{r github-packages, eval=FALSE}
# install.packages("remotes")
remotes::install_github("pbs-assess/gfdata")
remotes::install_github("pbs-assess/gfplot")
remotes::install_github("luke-a-rogers/ssio")
remotes::install_github("r4ss/r4ss")
remotes::install_github("Cole-Monnahan-NOAA/adnuts")
remotes::install_github("PIFSCstockassessments/ss3diags")
```

### Stock Synthesis 3.30

- Download the latest release of [Stock Synthesis 3.30](https://github.com/nmfs-ost/ss3-source-code?tab=readme-ov-file)
- Confirm that the ss3 executable is available in the R `$PATH`, for example using `r4ss::check_exe()`

## Fleets

Fleets are defined by a combination of `gear` type (e.g. "Hook and line") and 
`type` (e.g. "landings"). Because fleet definitions may differ between
models, data files for catch (catch.rds), indexes (index.rds), and lengths 
(length.rds) are stored (in data/ss3/) with `gear` and `type` columns,
to allow the analyst to define fleets specific to each model fit (typically in
ss3/xxx/00-fleets.R) in combination with the R package ssio (under development).

## Next steps

- [ ] Iterate fits in ss3/T00/ to explore base model options
- [ ] Develop base model in ss3/A00 using ss3/T00/ workflow
- [ ] Develop additional (sensitivity) model fits
